A flexible integer linear programming formulation for scheduling clinician on-call service in hospitals

### 2020-06-04 paper/paper.comparison.tex
Minor fixes to comparison section

In recent years, there has been a substantial amount of literature published in
the nurse rostering area aiming to organize the types of problems and approaches
commonly
addressed in the real-world. This research serves to highlight the similarities
and differences
among computationally easy and hard instances of nurse rostering, evaluating
which algorithms
are best geared towards which types of problems, and [...]

De Causmaecker and Berghe [ref] outline a categorization
of nurse rostering problems using a similar approach used in scheduling,
based around the personnel environment, work characteristics and optimization
objective. Previously, there was a lack of a central categorization for
nurse rostering problems found in the literature. Their work attempts
to address this, by creating a classification that takes into account
hard and soft constraints related to nurse preferences, consecutive 
assignments, coverage and various flexibilities in terms of shift and
skill types. They go on to describe where recent examples of the nurse rostering
literature can fit in their classification.

@@

[maybe 1 additional paragraph on categorization?]

We follow the work in [ref-De Causmaecker and Berghe] to place our clinician
scheduling problem
in the realm of work for nurse rostering. According to their specification, our
problem includes 
personnel environment constraints targeting the availability of clinicians
([list which constraints...]),
sequences of assignments ([...]), and balance of rosters ([...]) 
which fall under the categories $\alpha : A$, $\alpha : S$ and $\alpha : B$,
respectively. 
For work characteristics, the relevant category for our problem are the range
constraints, $\alpha : R$, 
as we restrict the workload of each clinician between a minimum and maximum
allowed blocks ([constraint...]).
Lastly, for the optimization objective our problem corresponds to the category
$\gamma : P$, as our optimization objective
aim to adhere to clinician preferences. Therefore the appropriate categorization
for our problem is $ASB/R/P$.

@@

In [ref-Bilgin 2008], Bilgin et al address a nurse rostering problem using local search. 
The problem presented is classified as $ASBI/RVNO/PLR$.
Some of the constraints they incorporate include coverage constraints, overlapping assignment
constraints and horizontal constraints, which include constraints arising from employment contracts
(such as satisfying minimum and maximum thresholds and limiting consecutive assignments). Unlike
our problem, Bilgin et al consider coverage constraints to be soft constraints, in order to prevent
over-constraining of the problem. They incorporate nurse requests into the model formulation,
similar to our problem, but they allow requests for both time off and time on.
[...]

>>>>

In recent years, there has been a substantial amount of literature published in
the nurse rostering area aiming to organize the types of problems and approaches
commonly
addressed in the real-world. This research serves to highlight the similarities
and differences
among computationally easy and hard instances of nurse rostering and evaluating
which algorithms
are best geared towards which types of problems thus allowing practitioners
to choose which approach will work best for their case.

De Causmaecker and Berghe [ref] outline a categorization
of nurse rostering problems using a similar approach used in theoretic scheduling problems,
based around the machine environment, job characteristics and constraints,
and optimization objective. Previously, there was a lack of a central categorization system
for nurse rostering problems found in the literature. Their work attempts
to address this by creating a classification that takes into account
hard and soft constraints related to nurse preferences, consecutive 
assignments, coverage and various flexibilities in terms of shift and
skill types. They go on to describe where recent examples of the nurse rostering
literature can fit in their classification.

@@

[maybe 1 additional paragraph on categorization systems?]

We follow the work in [ref-De Causmaecker and Berghe] to place our clinician
scheduling problem in the realm of work for nurse rostering. 
According to their specification, our problem includes 
personnel environment constraints targeting the availability of clinicians
([list which constraints...]),
sequences of assignments ([...]), and balance of rosters ([...]) 
which fall under the categories $\alpha : A$, $\alpha : S$ and $\alpha : B$,
respectively. 
For work characteristics, the relevant category for our problem are the range
constraints, $\beta : R$, 
as we restrict the workload of each clinician between a minimum and maximum
allowed blocks ([constraint...]).
Lastly, for the optimization objective our problem corresponds to the category
$\gamma : P$, as our optimization objective
aim to adhere to clinician preferences. Therefore the appropriate categorization
for our problem is $ASB/R/P$.

@@

In [ref-Bilgin 2008], Bilgin et al address a nurse rostering problem using local search. 
The problem presented is classified as $ASBI/RVNO/PLR$.
Some of the constraints they incorporate include coverage constraints, overlapping assignment
constraints and horizontal constraints, which include constraints arising from employment contracts
(such as satisfying minimum and maximum thresholds and limiting consecutive assignments). Unlike
our problem, Bilgin et al consider coverage constraints to be soft constraints, in order to prevent
over-constraining of the problem. They incorporate nurse requests into the model formulation,
similar to our problem, but they allow requests for both time off and time on.

[...]
